---
title: "Pre_Analysis_V1"
author: "GUI GAO & Chatpisut Magic Makornkhan"
date: "2023-08-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
library(tidyverse)
library(tidytext)
library(stringr)
library(lubridate)
library(ggplot2)
library(hms)
```


```{r}
ig_posts <- read.csv("clean_data/Instagram/ig_telco_posts.csv")
ig_comments <- read.csv("clean_data/Instagram/ig_telco_comments.csv")
fb_posts <- read.csv("clean_data/Facebook/fb_telco_posts.csv")
fb_comments <- read.csv("clean_data/Facebook/fb_telco_comments.csv")
```

# Analysis

# ----------- Content Analysis --------------- 
## Use wordcloud as the first step to get the idea of contents grouping
## Use Principal Components to group types of contents for posts and comments in order to categorize them into meaningful groups
## Find which groups related to other variables

# ----------- Date Time Analysis --------------- 
## Basic relationships of optimum and general date/time relationship with social media reactions

# ----------- Findings --------------- 
## Relationships of Date/Time to other variables and reactions
## Relationships of word cloud to reactions
## Search more on what client might want out of this
## Machine Learning on variables across others
## Brand auditing relative to time and their performance throughtout posts from past to recent
## Comparison between brands

## Basic Analysis Plan
## 1. WordCloud - Gui
## 2. Trends - Magic
## 3. Post Time - Magic
## 4. Post Date and Days - Gui

## ------------- Trend Analysis -------------
## ------------------ FB --------------------


```{r trends-FB}
## 2. Trends Analysis - Magic

fb_posts_adjusted <- fb_posts %>% 
  mutate(post_date = as.Date(post_date)) %>% 
  filter(reactions < 5000,
         shares < 300)
```


```{r trends2-FB}

fb_trend_analysis <- ggplot(fb_posts_adjusted, aes(x = post_date)) +
  #Reactions
  geom_line(aes(y = reactions, color = brand), linetype = "solid") +
  geom_point(aes(y = reactions, color = brand, shape = "reactions"), size = 2) +
  geom_hline(yintercept = 100, linetype = "dashed", color = "black", linewidth = 0.7) +  # Add line to distinguish low interaction posts
  #Comments
  geom_line(aes(y = comments, color = brand), linetype = "longdash") +
  geom_point(aes(y = comments, color = brand, shape = "comments"), size = 2) +
  #Shares
  geom_line(aes(y = shares, color = brand), linetype = "dotted") +
  geom_point(aes(y = shares, color = brand, shape = "shares"), size = 2) +
  labs(title = "Facebook Trend Analysis by Brand",
       x = "Date Post",
       y = "Magnitude") +
  scale_color_manual(values = c("Telstra" = "purple", "Optus" = "blue", "Vodafone Australia" = "red", "amaysim" = "orange")) +
  facet_wrap(~brand, ncol = 1, scales = "free_y") + # Use scales = "free_y" to make y-axis flexible
  theme_minimal()

```


## -------------- IG -----------------


```{r trends-IG}

ig_posts <- ig_posts %>%
  mutate(numbers = as.numeric(gsub(",", "", numbers)))

ig_posts_low5k <- ig_posts %>% 
  mutate(post_date = as.Date(post_date)) %>%
  filter(numbers <= 5000)
  
ig_posts_high5k <- ig_posts %>% 
  mutate(post_date = as.Date(post_date)) %>% 
  filter(numbers > 5000)

```

```{r trends2-IG}
ig_low_trend_analysis <- ggplot(ig_posts_low5k, aes(x = post_date)) +
  geom_line(aes(y = numbers, color = brand, linetype = interactions)) +
  geom_point(aes(y = numbers, color = brand, shape = interactions), size = 3) +
  geom_hline(yintercept = 100, linetype = "dashed", color = "black", linewidth = 0.7) +  # Add line to distinguish low interaction posts
  labs(title = "Instagram (Low Interactions Post) Trend Analysis by Brand",
       x = "Date Post",
       y = "Magnitutde") +
  scale_color_manual(values = c("Telstra" = "purple", "Optus" = "blue", "Vodafone Australia" = "red", "amaysim" = "orange")) +
  scale_linetype_manual(values = c("likes" = "solid", "views" = "dashed")) +
  scale_shape_manual(values = c("likes" = 16, "views" = 17)) +
  facet_wrap(~brand, ncol = 1, scales = "free_y") +  # Use scales = "free_y" to make y-axis flexible
  theme_minimal()

ig_high_trend_analysis <- ggplot(ig_posts_high5k, aes(x = post_date)) +
  geom_line(aes(y = numbers, color = brand, linetype = interactions)) +
  geom_point(aes(y = numbers, color = brand, shape = interactions), size = 3) +
  labs(title = "Instagram (High Interactions Post) Trend Analysis by Brand",
       x = "Date Post",
       y = "Magnitutde") +
  scale_color_manual(values = c("Telstra" = "purple", "Optus" = "blue", "Vodafone Australia" = "red", "amaysim" = "orange")) +
  scale_linetype_manual(values = c("likes" = "solid", "views" = "dashed")) +
  scale_shape_manual(values = c("likes" = 16, "views" = 17)) +
  facet_wrap(~brand, ncol = 1, scales = "free_y") +  # Use scales = "free_y" to make y-axis flexible
  theme_minimal()
```


## ------------- Post Time Analysis -------------
## ------------------ FB --------------------

```{r}
fb_posts$post_time <- as_hms(strptime(fb_posts$post_time, "%H:%M"))

fb_posttime_analysis <- ggplot(fb_posts, aes(x = post_time)) +
  #Reactions
  geom_line(aes(y = reactions, color = brand), linetype = "solid") +
  geom_point(aes(y = reactions, color = brand, shape = "reactions"), size = 2) +
  geom_hline(yintercept = 100, linetype = "dashed", color = "black", linewidth = 0.7) +  # Add line to distinguish low interaction posts
  #Comments
  geom_line(aes(y = comments, color = brand), linetype = "longdash") +
  geom_point(aes(y = comments, color = brand, shape = "comments"), size = 2) +
  #Shares
  geom_line(aes(y = shares, color = brand), linetype = "dotted") +
  geom_point(aes(y = shares, color = brand, shape = "shares"), size = 2) +
  labs(title = "Facebook Trend Analysis by Brand",
       x = "Date Post",
       y = "Magnitude") +
  scale_color_manual(values = c("Telstra" = "purple", "Optus" = "blue", "Vodafone Australia" = "red", "amaysim" = "orange")) +
  facet_wrap(~brand, ncol = 1, scales = "free_y") + # Use scales = "free_y" to make y-axis flexible
  theme_minimal()

## Limitations: All of these are not measured within a time limit as benchmark checking, but from the post date up to July 2023 - meaning that magnitude of interactions might not be pertaining solely on post_time at this point.
```


```{r}
fb_trend_analysis
ig_low_trend_analysis
ig_high_trend_analysis
fb_posttime_analysis
```



