---
title: "Pre_Analysis_V1"
author: "GUI GAO & Chatpisut Magic Makornkhan"
date: "2023-08-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(tidyverse)
library(tidytext)
library(stringr)
library(lubridate)
```


```{r}
IG_Telco_posts_clean <- read.csv("clean_data/Instagram/IG_Telco_posts.csv")
IG_Telco_comments_clean <- read.csv("clean_data/Instagram/IG_Telco_comments.csv")
FB_Telco_posts_clean <- read.csv("clean_data/Facebook/FB_Telco_posts.csv")
FB_Telco_comments_clean <- read.csv("clean_data/Facebook/FB_Telco_comments.csv")
FB_postcomt <- read.csv("clean_data/Facebook/fb_telco_postcomments.csv")
IG_postcomt <- read.csv("clean_data/Instagram/ig_telco_postcomments.csv")
```

## Cleaning Facebook Dataset

```{r}
FB_postcomt$post_date <- as.Date(FB_postcomt$post_date)

FB_comt <- FB_postcomt %>%
  select(post_url, comment_content) %>%
  aggregate(comment_content ~ post_url, FUN = paste, collapse = " ")

FB_number <- FB_postcomt %>%
  select(post_url, likes) %>%
  group_by(post_url) %>%
  mutate(likes = sum(likes))

FB_number[!duplicated(FB_number$post_url), ] -> FB_number
FB_postcomt[!duplicated(FB_postcomt$post_url), ] -> FB_postcomt

FB_postcomt <- FB_postcomt %>%
  select(!c(username, comment_content, likes, 
            comment_date, post_time_hr)) %>%
  left_join(FB_number, by = "post_url")

FB_postcomt <- FB_postcomt %>%
  left_join(FB_comt, by = "post_url")

FB_postcomt <- FB_postcomt %>%
  mutate(comment_content = ifelse(is.na(comment_content), "", comment_content))
```

## Cleaning Instagram Dataset

```{r}
IG_postcomt$numbers <- as.numeric(gsub(",", "", IG_postcomt$numbers))
IG_postcomt$post_date <- as.Date(IG_postcomt$post_date)

IG_comt <- IG_postcomt %>%
  select(post_url, content) %>%
  aggregate(content ~ post_url, FUN = paste, collapse = " ")

IG_number <- IG_postcomt %>%
  select(post_url, likes_number) %>%
  group_by(post_url) %>%
  mutate(likes_number = sum(likes_number))

IG_number[!duplicated(IG_number$post_url), ] -> IG_number
IG_postcomt[!duplicated(IG_postcomt$post_url), ] -> IG_postcomt

IG_postcomt <- IG_postcomt %>%
  select(!c(comment_username, content, date, 
            likes_number)) %>%
  left_join(IG_number, by = "post_url") %>%
  mutate(likes_number = ifelse(is.na(likes_number), 0, likes_number))

IG_postcomt <- IG_postcomt %>%
  left_join(IG_comt, by = "post_url")

IG_postcomt <- IG_postcomt %>%
  mutate(content = ifelse(is.na(content), "", content))
```


# Analysis

```{r}

```

# ----------- Content Analysis --------------- 
## Use wordcloud as the first step to get the idea of contents grouping
## Use Principal Components to group types of contents for posts and comments in order to categorize them into meaningful groups
## Find which groups related to other variables

# ----------- Date Time Analysis --------------- 
## Basic relationships of optimum and general date/time relationship with social media reactions

# ----------- Findings --------------- 
## Relationships of Date/Time to other variables and reactions
## Relationships of word cloud to reactions
## Search more on what client might want out of this
## Machine Learning on variables across others
## Brand auditing relative to time and their performance throughtout posts from past to recent
## Comparison between brands



