---
title: "Pre_Analysis_V1"
author: "GUI GAO & Chatpisut Magic Makornkhan"
date: "2023-08-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
library(tidyverse)
library(tidytext)
library(stringr)
library(lubridate)
```


```{r}
IG_Telco_posts_clean <- read.csv("clean_data/Instagram/IG_Telco_posts.csv")
IG_Telco_comments_clean <- read.csv("clean_data/Instagram/IG_Telco_comments.csv")
FB_Telco_posts_clean <- read.csv("clean_data/Facebook/FB_Telco_posts.csv")
FB_Telco_comments_clean <- read.csv("clean_data/Facebook/FB_Telco_comments.csv")
```

# Analysis

```{r}

```

# ----------- Content Analysis --------------- 
## Use wordcloud as the first step to get the idea of contents grouping
## Use Principal Components to group types of contents for posts and comments in order to categorize them into meaningful groups
## Find which groups related to other variables

# ----------- Date Time Analysis --------------- 
## Basic relationships of optimum and general date/time relationship with social media reactions

# ----------- Findings --------------- 
## Relationships of Date/Time to other variables and reactions
## Relationships of word cloud to reactions
## Search more on what client might want out of this



