---
title: "Sentiment Analysis_Magic"
author: "Chatpisut Makornkhan"
date: "2023-08-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(tidyverse)
library(tidytext)
library(stringr)
library(lubridate)
library(ggplot2)
library(wordcloud)
library(wordcloud2)
library(reshape2)
library(mice)
library(openai)
library(hms)
```


```{r}
ig_posts <- read.csv("clean_data/Instagram/ig_telco_posts.csv")
ig_comments <- read.csv("clean_data/Instagram/ig_telco_comments.csv")
fb_posts <- read.csv("clean_data/Facebook/fb_telco_posts.csv")
fb_comments <- read.csv("clean_data/Facebook/fb_telco_comments.csv")
fb_postcomt <- read.csv("clean_data/Facebook/fb_telco_postcomments.csv")
ig_postcomt <- read.csv("clean_data/Instagram/ig_telco_postcomments.csv")
```

## Comments' Common Words - General Sentiment Analysis from consumer; most common words toward brands -> brand perception
## Comments' Common Words - Mood and Tone -> categorized into positive and negative sentiment
## Lexicon dictionary - Pie Chart, by brand
## Tf-Idf - table with graphs


```{r}
fb_comments_tokens <- fb_comments %>%
  unnest_tokens(word, comment_content)
```

```{r}
ig_comments_tokens <- ig_comments %>%
  unnest_tokens(word, content)
```


# WordCloud Setting
```{r}
get_sentiments("bing")

stopword <- get_stopwords(source = "snowball")

colPalette <- c("#39A8AF", "#FECD03","#0060AE", "#0A8AD2", 
                "#e82f89", "#9b0082","#ef2d1e", "#FF5500")

```


## Facebook Comment WordCloud
```{r}

fb_comments_tokens %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 300))

#### --------------------------------------

## Facebook Word Tokens Setup

fb_comment_word <- fb_postcomt %>%
  mutate(id = row_number()) %>%
  select(id, brand, comment_content, username, likes, post_date, post_time_hr) %>%
  unnest_tokens(output = word,
                input = comment_content,
                token = "words") %>%
  anti_join(stopword, by = "word") %>%
  filter(!str_detect(word, '^[[:digit:]]'))

## General WordCloud
fb_comment_word %>%
  group_by(word) %>%
  summarise(freq = n()) %>%
  top_n(150) %>%
  wordcloud2(color = rep_len(colPalette, nrow(fb_comment_word)),
             size = 0.6,
             shape = "circle")

## Positive-Negative WordCloud
fb_comment_word %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)

## By Brand

### Telstra
fb_comment_word %>%
  filter(brand == "Telstra") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)

### Optus
fb_comment_word %>%
  filter(brand == "Optus") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)

### Vodafone Australia
fb_comment_word %>%
  filter(brand == "Vodafone Australia") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)

### amaysim
fb_comment_word %>%
  filter(brand == "amaysim") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)

```


## Instagram Comment WordCloud
```{r}
## General WordCloud
ig_comment_word <- ig_postcomt %>%
  mutate(id = row_number()) %>%
  select(id, brand, comment_username, content, likes_number, date) %>%
  unnest_tokens(output = word,
                input = content,
                token = "words") %>%
  anti_join(stopword, by = "word") %>%
  filter(!str_detect(word, '^[[:digit:]]'))


## General WordCloud
ig_comment_word %>%
  group_by(word) %>%
  summarise(freq = n()) %>%
  top_n(150) %>%
  wordcloud2(color = rep_len(colPalette, nrow(ig_comment_word)),
             size = 0.6,
             shape = "circle")


## Positive-Negative WordCloud
ig_comment_word %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)

## By Brand
### Telstra

ig_comment_word %>%
  filter(brand == "Telstra") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)
  
### Optus

ig_comment_word %>%
  filter(brand == "Optus") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)
  
### Vodafone Australia

ig_comment_word %>%
  filter(brand == "Vodafone AU") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)
  
### amaysim

ig_comment_word %>%
  filter(brand == "amaysim") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = T) %>%
  reshape2::acast(word ~ sentiment, 
                  value.var = "n",
                  fill = 0) %>%
  comparison.cloud(colors = c("#c30101", "lightgreen"),
                   max.words = 150)
```

# Checking missing values
```{r}
md.pattern(fb_posts)
md.pattern(fb_comments)
md.pattern(ig_posts)
md.pattern(fb_comments)
```
